Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
discuss timescales, adapt wording of caveats

\rev{\citet{Ranjan2017b} speculated that UV photochemistry might be rate-limiting for abiogenesis, particularly on planets orbiting M dwarfs, due to their low baseline UV fluxes.
This could delay abiogenesis by orders of magnitude, resulting in a continuous dependence of abiogenesis likelihood on UV flux.
However, recent studies challenge this view for the cyanosulfidic scenario.
\citet{Rimmer2021} calculated photochemical timescales on early Earth at 180--300 hours (7.5--12.5 days), significantly shorter than the timescale for stochastic geological events also required for the scenario~\citep{Rimmer2023}.
Even with 1000x slower photochemistry on M-dwarf planets, prebiotic photochemistry like sulfite photolysis would still occur on a geologically negligible timescale of 20--30 years, meaning that the photochemistry is unlikely to be rate limiting compared to stochastic geological processes, justifying the step-function model.
}

\rev{Nonetheless, alternative abiogenesis pathways or combinations of pathways may exhibit continuous or mixed dependencies on UV flux.
While the step-function formalism is justified for the cyanosulfidic scenario, future work should explore UV dependencies across other scenarios to refine predictions for biosignature distributions and testable hypotheses.
}

>>>>

\rev{\citet{Ranjan2017b} speculated that UV photochemistry might be rate-limiting for abiogenesis, particularly on planets orbiting M dwarfs, due to their low baseline UV fluxes.
This could delay abiogenesis by orders of magnitude, resulting in a continuous dependence of abiogenesis likelihood on UV flux.
However, recent studies challenge this view for the cyanosulfidic scenario.
\citet{Rimmer2021} calculated photochemical timescales on early Earth at 180--300 hours (7.5--12.5 days), significantly shorter than the timescale for stochastic geological events also required for the scenario~\citep{Rimmer2023}.
Even with 1000x slower photochemistry on M-dwarf planets, prebiotic photochemistry like sulfite photolysis would still occur on a geologically negligible timescale of 20--30 years, meaning that the photochemistry is unlikely to be rate limiting compared to stochastic geological processes, justifying the step-function model.
}
\revv{We note that the photochemical timescale does not include subsequent stages such as assembly into functional biomolecules, protocell formation, or the emergence of self-replicating systems -- each of which may require significantly more time.
However, in the context of the cyanosulfidic scenario, UV irradiation is needed only for this initial synthetic step, and later stages can proceed under different environmental conditions, potentially long after UV levels have declined.
Moreover, abiogenesis may require many ``failed trials'', we effectively control for this uncertainty by requiring that both sufficient UV flux and habitable conditions persist for a minimum duration $\Delta T_\mathrm{min}$.
We further require that the planet remains in the habitable zone at the time of observation, thereby capturing both the origination and persistence phases encapsulated by $f_\mathrm{life}$.
}

\rev{Nonetheless, alternative abiogenesis pathways or combinations of pathways may exhibit continuous or mixed dependencies on UV flux.}
\revv{Future work} should explore UV dependencies across other scenarios to refine predictions for biosignature distributions and testable hypotheses.
